Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-06-20 Thesis/chapter/03-theoretical-background.tex
freewriting AI

The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
%the best humans don't stand a chance against the best computers since \td{early 2000s}).\cite{Silver2017}
Another test ingenioussed by Alan Turing, is that a human who communicates with a unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
It is easy for humans to come up with question to detect and AI, 
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.

But fear not, that doesn't mean that computers are more intelligent than humans and certainly not that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
it is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
Now, we can't - it's hard to - imagine to live without electricity. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017}, 
image recognition (in medicine)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
in chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition to prevent theft of toilet paper \cite{Andrews2017},
financial sector (as robo-advisors)\cite{Littman2021}
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021}
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create artwork (DALL-E 2)\cite{Marcus2022} or 
making video games \cite{Guzdial2016}
.
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice and after some time of general use are no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai (Google CEO) even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}

%which fields will be incorporated by AI in the near future? 
%which questions have to be answered? philosophical and ethical questions. 
%Humans, now, must mit sich selbst auseinaner setzen 
%

\subsubsection{AI vs statistics}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsubsection{Design of Experiment}

>>>>

The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
%the best humans don't stand a chance against the best computers since \td{early 2000s}).\cite{Silver2017}
Another test ingenioused by Alan Turing, is that a human who communicates with a unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
It is easy for humans to come up with question to detect an AI, 
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.

But fear not, that doesn't mean that computers are more intelligent than humans\cite{searle1999married,searle1980} and certainly not that research is over. 
AI is still a young field, which is strongly growing and is gaining ubiquitous status. 
It is slowly creeping into every aspect of modern human life just like electricity around one hundred years ago. 
%Now, we can't - it's hard to - imagine to live without electricity. 
Realms in which AI is gaining traction are: 
%
playing board games (and beating humans)\cite{Silver2017}, 
image recognition (in medicine)\cite{Li2020,Deo2015,Topol2019,Fujiyoshi2019}, 
in chemistry\cite{Westermayr2019,goh2017chemception,jha2018elemnet}, 
cyber security\cite{Sarker2021},
facial recognition to prevent theft of toilet paper \cite{Andrews2017},
financial sector (as robo-advisors)\cite{Littman2021}
natural language processing (NLP)\cite{Koroteev2021,Liu2021gpt,Parviainen2021}
and even creative tasks like 
creating non existing faces\cite{Mansourifar2020}, 
create artwork (DALL-E 2)\cite{Marcus2022} or 
making video games \cite{Guzdial2016}
.
It is nearly hard to find a field where \gls{ai} isn't used in some way. 
This steady incorporation of \gls{ai} leads to the so called \gls{ai} effect\cite{McCorduck1982,ai100}: 
certain fields get incorporated into \gls{ai} research and practice and after some time of general use are no more considered \gls{ai} (e.g. spam filter or web searches).
Google CEO Sundar Pichai (Google CEO) even goes as far and said: 
"AI is one of the most important things humanity is working on. It is more profound than [...] electricity or fire"\cite{Hassan2020}

%which fields will be incorporated by AI in the near future? 
%which questions have to be answered? philosophical and ethical questions. 
%Humans, now, must mit sich selbst auseinaner setzen 
%
\subsubsection{Free writing about AI}
I chose an evolutionary algorithm which is - i think - also part of machine learning, 
which is a part of AI. 
There are many different types of AI. what are the most haeufig sub domains of the AI field? 
(natural) language processing, image erkennung, and prediction which can be geteilt in 
classification (discrete) and continuous prediction. 
These are mainly machine learning algos. other machine learning tasks are EA, PSO,

\subsubsection{AI vs statistics}
let GPT-3 write 
check out links at \url{https://yewtu.be/watch?v=PqbB07n_uQ4}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsubsection{Design of Experiment}
